\renewcommand{\abstractname}{} % Remove default abstract title
\begin{adjustwidth}{-0.35in}{-0.35in}
\begin{abstract}
\noindent \textbf{\Huge Abstract} \\[0.5em] % Title in large font


\noindent
This study, conducted as part of a summer placement on massive star models, provides a comprehensive analysis of nuclear reaction networks, initial metallicities, and convective boundary mixing and their influence on stellar evolution and the final fates of stars as supernovae, neutron stars, or black holes. Understanding these factors is critical for unraveling the life cycles and ultimate fates of stars. Specifically, these elements play a pivotal role in determining stellar luminosity, lifespan, and nucleosynthetic yields. Such characteristics not only affect the individual stars but also have broader implications for galactic chemical enrichment and the formation of subsequent generations of stars and planets.

\vspace{1em}
\noindent
The evolutionary models presented in this research were generated using the latest version (r24.03.1) of the MESA code. We examine the evolution of a \(20 \, M_\odot\) star model across various nuclear networks, including \texttt{approx21\_cr60\_plus\_co56.net}, \texttt{o\_burn\_full.net}, \texttt{mesa\_128.net}, and \texttt{mesa\_206.net}, to evaluate their differential effects on stellar evolution. In addition, we utilize the simplest nuclear network, \texttt{approx21\_cr60\_plus\_co56.net}, alongside three distinct initial masses—15, 20, and 25 \( M_\odot \)—across a range of metallicities (\( Z = Z_\odot \) to \( Z = 10^{-7} \) and \( Z = 0 \)). This multifaceted approach aids in understanding how mass and metallicity interactively influence stellar evolution.

\vspace{1em}
\noindent
Furthermore, we investigate the mechanisms of energy transport within stars by examining convective boundary mixing (CBM). By applying varying rates of CBM to our stellar models, we gain valuable insights into its significant role in shaping stellar structures and evolutionary pathways. The findings of this study enhance our understanding of the complexities involved in stellar evolution and contribute to the broader knowledge of astrophysical processes.
\end{abstract}
\end{adjustwidth}
